A data-intensive assessment of the species-abundance distribution.

### 2015-03-17 defense_pres.tex
Sets font color to match the blue in the USU Ecology Center logo.
Should set all the normal text to USU Blue also.
Works on presentation; adds frametitles.
Adds sections, subsections, and table.

\documentclass{beamer}
\usetheme{Pittsburgh}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{tgbonum}
\usepackage{amssymb}
\usepackage{graphicx}
\usefonttheme{structuresmallcapsserif}
\usefonttheme{serif}
\author{Elita Baldridge}
\title[17pt]{A data-intensive assessment of the species-abundance distribution.}
\setbeamertemplate{navigation symbols}{}
\date{}
%\setbeamercovered{transparent} 
%\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
\institute{\includegraphics[scale=.07]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.1]{../Miscellaneous/Pictures/Weecology.png}} 
%\subject{} 
\begin{document}

@@

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter2/bioregions.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter2/taxa_sites.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter2/num_taxa.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter1/AICc_weights.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter1/likelihoods.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.5]{./sad-data/chapter1/likelihoods_one_to_one.png}
\end{frame}

\begin{frame}{}
\includegraphics[scale=.3]{./sad-data/chapter3/distabclasses_vs_lognormwgt.png}
\end{frame}

>>>>

\documentclass[17pt]{beamer}
\usetheme{Pittsburgh}
\usepackage{xcolor}
\definecolor{USUBlue}{RGB}{26,57,89}
\usecolortheme[named=USUBlue]{structure}
\setbeamercolor{normal text}{fg=USUBlue}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{tgbonum}
\usepackage{amssymb}
\usepackage{graphicx}
\usefonttheme{structuresmallcapsserif}
\usefonttheme{serif}
\setbeamercolor{author}{fg=USUBlue}
\setbeamerfont{author}{size=\small}
\setbeamerfont{frametitle}{size=\small}
\author{Elita Baldridge}
\title[17pt]{A data-intensive assessment of the species-abundance distribution.}
\setbeamertemplate{navigation symbols}{}
\date{}
%\setbeamercovered{transparent} 
%\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
\institute{\includegraphics[scale=.07]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.1]{../Miscellaneous/Pictures/Weecology.png}} 
%\subject{} 
\begin{document}

@@

\section{Data}

\subsection{Compiled Data}
\subsubsection{Data Collection}
\begin{frame}[shrink=30]
\frametitle{Data}
\begin{table}
\begin{tabular}{l|l} 
 Variable name & Variable definitions\\ 
\hline
 Class & Taxonomic class of species \\
 Family & Taxonomic family of species \\
 Genus & Taxonomic genus of species\\
 Species & Specific epithet of species  \\
 Relative\_abundance & Relative abundance of species \\
 Abundance & Abundance of species \\
 Collection\_Year & Start of collecting \\
 End\_Collection & End of collecting \\
 Site\_Name & Name/description of site \\
 Biogeographic\_region & Biogeographic region \\
 Site\_notes & Additional site information \\ 
\end{tabular}
\caption{List of variables collected.}
\end{table}
\end{frame}

\subsubsection{Data Summary}
\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.5]{./sad-data/chapter2/bioregions.png}
\end{frame}

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.5]{./sad-data/chapter2/taxa_sites.png}
\end{frame}

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.5]{./sad-data/chapter2/num_taxa.png}
\end{frame}

\subsection{Additional Data}

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.5]{./sad-data/chapter3/partial_sites_map.png}
\end{frame}

\section{Species abundance distribution comparisons}
\subsection{Analysis}
\subsection{Results}
\begin{frame}{}
\frametitle{Abundance distribution Comparisons}
\includegraphics[scale=.5]{./sad-data/chapter1/AICc_weights.png}
\end{frame}

\begin{frame}{}
\frametitle{Abundance distribution Comparisons}
\includegraphics[scale=.5]{./sad-data/chapter1/likelihoods.png}
\end{frame}

\begin{frame}{}
\frametitle{Abundance distribution Comparisons}
\includegraphics[scale=.5]{./sad-data/chapter1/likelihoods_one_to_one.png}
\end{frame}

\section{Neutral analysis}
\subsection{Analysis}
\subsection{Results}
\begin{frame}{}
\frametitle{Neutral Analysis}
\includegraphics[scale=.25]{./sad-data/chapter3/distabclasses_vs_lognormwgt.png}
\end{frame}

\begin{frame}{}
\frametitle{Neutral Analysis}
\includegraphics[scale=.6]{./sad-data/chapter3/avgvals_by_dataset.png}
\end{frame}

\section{Conclusions}

\section{Acknowledgements}
\subsection{Accessibility}
